\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{graphicx}%
\usepackage{fancyhdr}
\usepackage{fullpage}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}
\usepackage{multirow}
\usepackage{color}
\usepackage{enumitem}
\usepackage[top=4cm, bottom=4cm]{geometry}

\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages

\newenvironment{myindentpar}[1]%
{\begin{list}{}%
         {\setlength{\leftmargin}{#1}}%
         \item[]%
}
{\end{list}}

\renewcommand\refname{\vspace{-0.4in}}
\textwidth5in
\addtolength{\topmargin}{-\headsep}
\setlength{\oddsidemargin}{0in}
\oddsidemargin 0.75in \evensidemargin 0.75in
\setlength{\parindent}{0pt}
\newcounter{list}

\fancypagestyle{firststyle}
{
   \fancyhf{}
   \renewcommand{\headrulewidth}{0pt}
   \fancyhead[R]{\vspace{-2cm}\footnotesize Last updated May 15, 2022}
}

\newcommand{\hide}[1]{}

\begin{document}

\setcounter{secnumdepth}{0}

\thispagestyle{firststyle}

\section{\LARGE{\sc Meng Jiang, Ph.D.}}
University of Notre Dame \hfill \url{http://www.meng-jiang.com/} \\
326C Cushing Hall \hfill \url{mjiang2@nd.edu}\\
Notre Dame, IN 46556 \hfill +1 (574) 631--7454

\subsection{\sc Work Experience}
\vspace{-0.4cm} \line(1,0){370} \vspace{0.1cm}

\begin{table}[h!]
\begin{tabular*}{12.7cm}{p{10.0cm}p{3.25cm}r}
\bf{Assistant Professor}&2017 -- \textit{present}\\
 \multicolumn{2}{l}{~{University of Notre Dame}}\\
 \multicolumn{2}{l}{~{Department of Computer Science and Engineering}}\\
\\
\bf{Postdoctoral Research Associate}&2015 -- 2017\\
 \multicolumn{2}{l}{~{University of Illinois at Urbana-Champaign}}\\
 \multicolumn{2}{l}{~{Department of Computer Science}} \\
 \multicolumn{2}{l}{~{Advisor: Prof. Jiawei Han}} \\	
\end{tabular*}
\end{table}
\vspace{-0.4cm}

\vspace{-0.2cm}
\subsection{\sc Education}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{table}[h!]
\begin{tabular*}{12.7cm}{p{1.15cm}p{10.00cm}r}
\bf{Ph.D.}&Tsinghua University, Computer Science and Technology&2015\\
 &\multicolumn{2}{l}{Dissertation: \textit{Modeling Complex User Behaviors on Social Media}}\\
 &\multicolumn{2}{l}{Graduated with honors; Advisor: Prof. Shiqiang Yang}\\
 &\multicolumn{2}{l}{Visiting Ph.D. Student at CMU; Advisor: Prof. Christos Faloutsos}\\	
\bf{B.Eng.}&Tsinghua University, Computer Science and Technology&2010

\end{tabular*}
\end{table}

\vspace{-0.6cm}
\subsection{\sc Honors and Awards}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{table}[h!]
\begin{tabular*}{12.7cm}{p{11.65cm}r}
NSF CAREER Award & 2022 \\
ACM CIKM Conference Best Reviewer Award & 2021 \\	
ACM SIGSOFT (ICSE) Distinguished Paper Award & 2021 \\
ACM SIGKDD-DLG Workshop Best Paper Award & 2020 \\
ISDSA Annual Meeting Best Paper Award & 2020 \\
ACM WSDM Conference Outstanding PC Award & 2020 \\
NSF CRII Award & 2019 \\
Notre Dame Faculty Research Award & 2019 \\
ACM SIGKDD Conference ``Best of KDD 2014'' & 2014 \\
\end{tabular*}
\end{table}

\vspace{-0.6cm}
\subsection{\sc Scholar Pages}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{table}[h!]
\begin{tabular*}{12.7cm}{p{11.65cm}r}
\multicolumn{2}{l}{Google Scholar: \url{https://scholar.google.com/citations?user=LZIPfCkAAAAJ}} \\
~~~~~Citations & 3655 \\
~~~~~h-index & 30 \\
~~~~~i10-index & 61 \\
\multicolumn{2}{l}{DBLP: \url{https://dblp.org/pers/hd/j/Jiang\_0001:Meng}} \\
\end{tabular*}
\end{table}

\subsection{\sc Grants and Gifts}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}External funds: Total amount: \$3,523,052; Total credit: \textbf{\$1,880,704}

\hspace{-0.75cm}``CAREER: Synergistic Approaches for Specialized Intelligent Assistance'' \\
March 15, 2022 -- February 28, 2027 \\
Funding Vehicle: NSF IIS-2142827 \\
Amount: \textbf{\$549,969} (Credit: 100\%) \\
Role: {Sole PI}

\hspace{-0.75cm}``III: Small: Comprehensive Methods to Learn to Augment Graph Data'' \\
March 1, 2022 -- February 28, 2025 \\
Funding Vehicle: NSF IIS-2146761 \\
Amount: \textbf{\$499,999} (Credit: 100\%) \\
Role: {Sole PI}

\hspace{-0.75cm}``CRII: III: Beyond Similarity Learning: Complementarity Learning for Contextual Behavior Modeling'' \\
October 1, 2019 -- September 30, 2021 (\emph{Completed}) \\
Funding Vehicle: NSF IIS-1849816 \\
Amount: \textbf{\$174,910} (Credit: 100\%) \\
Role: {Sole PI}

\hspace{-0.75cm}``RETTL: Collaborative Research: Advancing STEM Online Learning by Augmenting Accessibility with Explanatory Captions and AI'' \\
September 15, 2021 -- August 31, 2024 \\
Funding Vehicle: NSF IIS-2119531 \\
Amount: \$849,994 (Credit: 22\%; \textbf{\$190,070}) \\
Role: {ND Lead PI}

\hspace{-0.75cm}``SHF: Medium: Collaborative Research: Semantically-Enhanced Software Traceability for Supporting Human-Centric Tasks'' \\
August 15, 2019 -- August 14, 2023 \\
Funding Vehicle: NSF CCF-1901059 \\
Amount: \$1,035,030 (Credit: 33\%; \textbf{\$341,556}) \\
Role: {Co-PI}

\hspace{-0.75cm}``Representation Learning for Modeling and Predicting User Engagement and Propensity for Conversion Through the Engagement Funnel'' \\
January 21, 2019 -- May 20, 2020 (\emph{Completed}) \\
Funding Vehicle: Conde Nast \\
Amount: \$148,400 (Credit: 50\%; \textbf{\$74,200}) \\
Role: {Co-PI}


\hspace{-0.75cm}``Advancing Real-Time Suicide Risk Detection Through the Digital Phenotyping Smartphone Application Screenomics'' \\
March 4, 2022 -- February 28, 2023 \\
Funding Vehicle: NIH 1R21MH129688-01 \\
Amount: \$234,750 (Credit: 8.5\%; \textbf{\$20,000}) \\
Role: {Co-Investigator}

\newpage
\hspace{-0.75cm}Unrestricted Gift: ``Automated Graph Data Augmentation with Reinforcement Learning''\\
September 28, 2021 \\
Funding Vehicle: Amazon \\
Amount: \textbf{\$20,000}

\hspace{-0.75cm}Unrestricted Gift: ``Augmenting Graph Data with Sequence Predictor'' \\
July 1, 2020 \\
Funding Vehicle: Snap Inc. \\
Amount: \textbf{\$10,000}

\hspace{-0.75cm}Internal Fund: ``Machine Learning Methods for Handling Nonlinear Relationships in Psychometric Models'' \\
June 1, 2022 -- August 15, 2023 \\
Funding Vehicle: Lucy Family Institute for Data \& Society \\
Amount: \$31,000 (Credit: 33\%; \textbf{\$10,230}) \\
Role: {co-PI}

\hspace{-0.75cm}Internal Fund: ``Explaining Recommender Systems with Counterfactual Examples''\\
January 1, 2022 -- December 31, 2022 \\
Funding Vehicle: Notre Dame International - Asia Collaboration Grant \\
Amount: \textbf{\$8,400} \\
Role: {Sole PI}

\hspace{-0.75cm}Internal Fund: ``Digital Empires: Structured Biographical and Social Network Analysis of Early Chinese Empires'' \\
May 1, 2019 -- August 31, 2021 (\emph{Completed}) \\
Funding Vehicle: Notre Dame International - Faculty Research Award \\
Amount: \$43,811 (Credit: 75\%; \textbf{\$33,281}) \\
Role: {ND CSE Lead PI}

\end{myindentpar}

\vspace{-0.6cm}
\subsection{\sc {\small \textit{(@ indicates supervised graduate students. * indicates supervised undergraduate students.)}}}
\subsection{\sc Publications}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.00cm}

\hspace{-0.25cm}\textit{Conference Papers} {\small (12 ACM SIGKDD full papers, etc.)}

\begin{enumerate}[leftmargin=.5cm]

\item[C68] @Zhao, T., @Liu, G., @Wang, D., @Yu, W., \textbf{Jiang, M.} ``Learning from Counterfactual Graph for Link Prediction'', in Proceedings of \textit{International Conference on Machine Learning} (ICML), 2022. (Acceptance rate 21.9\% = 1235/5630)

\item[C67] Gu, S., \textbf{Jiang, M.}, Guzzi, P.H., Milenkovic, T. ``Protein Functional Prediction via Multi-scale Data Integration'', in the \textit{Conference on Intelligent Systems for Molecular Biology} (ISMB), 2022. (Abstract)

\item[C66] Du, Y., Landers, R., Zhang, Y., \textbf{Jiang, M.} ``Intelligent Process Planning and Control of an Aerosol Jet Printing Process'', in the \textit{Annual International Solid Freeform Fabrication Symposium} (SFF Symp), 2022. (Abstract)

\item[C65] @Yu, W., Zhu, C., Qin, L., @Zhao, T. \textbf{Jiang, M.} ``Diversifying Content Generation for Commonsense Reasoning with Mixture of Knowledge Graph Experts'', in Findings of \textit{Annual Meeting of the Association for Computational Linguistics} (ACL), 2022.

\item[C64] @Yu, W., Zhu, C., Fang, Y., Yu, D., Wang, S., Xu, Y., Zeng, M., \textbf{Jiang, M.} ``Dict-BERT: Enhancing Language Model Pre-training with Dictionary'', in Findings of \textit{Annual Meeting of the Association for Computational Linguistics} (ACL), 2022.

\item[C63] *Kuebler, J., @Tong, L., \textbf{Jiang, M.} ``Multi-Round Parsing-based Multiword Rules for Scientific Knowledge Extraction'', in Proceedings of \textit{IEEE International Conference on Big Knowledge} (ICBK), 2021.
		
\item[C62] @Wang, D., @Zhao, T., Chawla, N.V., \textbf{Jiang, M.} ``Dynamic Attributed Graph Prediction with Conditional Normalizing Flows'', in Proceedings of \textit{International Conference on Data Mining} (ICDM), 2021. (Acceptance rate 20.0\% = 198/990)

\item[C61] @Yu, W., Zhu, C., @Zhao, T., Guo, Z., \textbf{Jiang, M.} ``Sentence-Permuted Paragraph Generation'', in Proceedings of \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2021. (Poster; acceptance rate 25.6\% = 650/2540)

\item[C60] *Dong, X., @Yu, W., Zhu, C., \textbf{Jiang, M.} ``Injecting Entity Types into Entity-Guided Text Generation'', in Proceedings of \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2021. (Short paper, selected for oral presentation; acceptance rate 6.2\% = 66/1060)

\item[C59] @Zhao, T., *Ni, B., @Yu, W., Guo, Z., Shah, N., \textbf{Jiang, M.} ``Action Sequence Augmentation for Early Graph-based Anomaly Detection'', in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), 2021. (Acceptance rate 21.7\% = 271/1251)
		
\item[C58] @Zeng, Q., Lin, J., Yu, W., Cleland-Huang, J., \textbf{Jiang, M.} ``Enhancing Taxonomy Completion with Concept Generation via Fusing Relational Representations'', in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2021. (Acceptance rate 15.4\% = 238/1541)

\item[C57] \textbf{Jiang, M.} ``Cross-Network Learning with Partially Aligned Graph Convolutional Networks'', in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2021. (Acceptance rate 15.4\% = 238/1541)	

\item[C56] @Yu, W., Wu, L., @Zeng, Q., Deng, Y., Mahindru, R., Guven, S., \textbf{Jiang, M.} ``Technical Question Answering across Tasks and Domains'', in Proceedings of \textit{Conference of the North American Chapter of the Association for Computational Linguistics - Human Language Technologies} (NAACL-HLT), 2021. (Acceptance rate 19.5\% = 350/1797)

\item[C55] Zhu, C., Hinthorn, W., Xu, R., @Zeng, Q., Zeng, M., Huang, X., \textbf{Jiang, M.} ``Enhancing Factual Consistency of Abstractive Summarization'', in Proceedings of \textit{Conference of the North American Chapter of the Association for Computational Linguistics - Human Language Technologies} (NAACL-HLT), 2021. (Acceptance rate 19.5\% = 350/1797)

\item[C54] @Wang, D., Shiralkar, P., Lockard, C., Huang, B., Dong, X.L., \textbf{Jiang, M.} ``TCN: Table Convolutional Network for Web Table Interpretation'', in Proceedings of \textit{The Web Conference} (TheWebConf), 2021. (Acceptance rate 20.6\% = 357/1736)

\item[C53] Guo, Z., Zhang, C., @Yu, W., Herr, J., Wiest, O., \textbf{Jiang, M.}, Chawla, N.V. ``Few-Shot Graph Learning for Molecular Property Prediction'', in Proceedings of \textit{The Web Conference} (TheWebConf), 2021. (Acceptance rate 20.6\% = 357/1736)

\item[C52] Lin, J., Liu, Y., @Zeng, Q., \textbf{Jiang, M.}, Cleland-Huang, J. ``Traceability Transformed: Generating More Accurate Links with Pre-trained BERT Models'', in Proceedings of \textit{International Conference on Software Engineering} (ICSE), 2021. (Acceptance rate 22.4\% = 138/615; selected for \textbf{ACM SIGSOFT Distinguished Paper Award})

\item[C51] @Zhao, T., Liu, Y., Woodford, O., Neves, L., \textbf{Jiang, M.}, Shah, N. ``Data Augmentation for Graph Neural Networks'', in Proceedings of \textit{AAAI Conference on Artificial Intelligence} (AAAI), 2021. (Acceptance rate 21.4\% = 1692/7911)

\item[C50] Schnur, J., Karl, R., Garcia-Martinez, A., \textbf{Jiang, M.}, Chawla, N.V. ``Imputing Growth Snapshot Similarity in Early Childhood Development: A Tensor Decomposition Approach'', in Proceedings of \textit{IEEE International Conference on Bioinformatics and Biomedicine} (BIBM), 2020. (Acceptance rate 19.4\% = 111/572)

\item[C49] Jiang, T., Zhang, N., Liu, M., \textbf{Jiang, M.}, Liu, T., Qin, B. ``Use of Internal Knowledge: Biomedical Literature Search Liberated From External Resources'', in Proceedings of \textit{IEEE International Conference on Bioinformatics and Biomedicine} (BIBM), 2020. (Acceptance rate 19.4\% = 111/572)

\item[C48] Syed, M., @Wang, D., \textbf{Jiang, M.}, Conway, O., Juneja, V., Subramanian, S., Chawla, N.V. ``Overcoming Data Sparsity in Predicting User Characteristics from Behavior through Graph Embeddings'', in Proceedings of \textit{The IEEE/ACM International Conference on Advances in Social Networks Analysis and Mining} (ASONAM), 2020.

\item[C47] @Yu, W., Wu, L., Deng, Y., Mahindru, R., @Zeng, Q., Guven, S., \textbf{Jiang, M.} ``A Technical Question Answering System with Transfer Learning'', in Proceedings of \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2020. (Demo)
		
\item[C46] @Zeng, Q., @Yu, W., *Yu, M., @Jiang, T., Weninger, T., \textbf{Jiang, M.} ``Tri-Train: Automatic Pre-fine Tuning between Pre-training and Fine-tune Training for SciNER'', in Findings of \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2020. (Acceptance rate 34.6\% = 1274/3677)

\item[C45] Zhang, C., Yu, L., Saebi, M., \textbf{Jiang, M.}, Chawla, N.V. ``Few-Shot Multi-Hop Relation Reasoning over Knowledge Bases'', in Findings of \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2020. (Acceptance rate 34.6\% = 1274/3677)

\item[C44] Guo, Z., @Yu, W., Zhang, C., \textbf{Jiang, M.}, Chawla, N.V. ``GraSeq: Graph and Sequence Fusion Learning for Molecular Property Prediction'', in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2020. (Acceptance rate 21\% = 193/920)
		
\item[C43] @Zhao, T., *Deng, C., *Yu, K., @Jiang, T., @Wang, D., \textbf{Jiang, M.} ``Error-bounded Graph Anomaly Loss for GNNs'', in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2020. (Acceptance rate 21\% = 193/920)

\item[C42] Liu, Y., Lin, J., @Zeng, Q., \textbf{Jiang, M.}, Cleland-Huang, J. ``Towards Semantically Guided Traceability'', in Proceedings of \textit{IEEE International Requirements Engineering Conference} (RE), August 2020.	

\item[C41] @Wang, D., \textbf{Jiang, M.}, Syed, M., Conway, O., Juneja, V., Subramanian, S., Chawla, N.V. ``Calendar Graph Neural Networks for Modeling Time Structures in Spatiotemporal User Behaviors'', in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2020. (Selected for oral presentation; acceptance rate 5.8\% = 44/756)

\item[C40] @Yu, W., Wu, L., @Zeng, Q., Tao, S., Deng, Y., \textbf{Jiang, M.} ``Crossing Variational Autoencoders for Answer Retrieval'', in Proceedings of \textit{Annual Meeting of the Association for Computational Linguistics} (ACL), July 2020.

\item[C39] \textbf{Jiang, M.} ``Improving Situational Awareness with Collective Artificial Intelligence over Knowledge Graphs'', in Proceedings of \textit{Artificial Intelligence and Machine Learning for Multi-Domain Operations Applications II} in \textit{SPIE Defense + Commercial Sensing} Symposium, April 2020.

\item[C38] @Yu, W., *Yu, M., @Zhao, T., \textbf{Jiang, M.} ``Identifying Referential Intention with Heterogeneous Contexts'', in Proceedings of \textit{The Web Conference} (TheWebConf), April 2020. (Acceptance rate 19\% = 217/1129)

\item[C37] @Yu, W., *Peng, W., *Shu, Y., @Zeng, Q., \textbf{Jiang, M.} ``Experimental Evidence Extraction in Data Science with Hybrid Table Features and Ensemble Learning'', in Proceedings of \textit{The Web Conference} (TheWebConf), April 2020. (Acceptance rate 19\% = 217/1129; selected for \textbf{Best Poster Award} at the 14th Annual Poster Contest at ND CSE)

\item[C36] Tang, P., \textbf{Jiang, M.}, Xia, N., Pitera, J., Welser, J., Chawla, N.V. ``Multi-label Patent Categorization with Non-local Attention-based Graph Convolutional Network'', in Proceedings of \textit{AAAI Conference on Artificial Intelligence} (AAAI), February 2020. (Acceptance rate 20.6\% = 1591/7737)
	
\item[C35] Zhang, C., Yao, H., \textbf{Jiang, M.}, Li, Z., Chawla, N.V. ``Few-Shot Knowledge Base Completion'', in Proceedings of \textit{AAAI Conference on Artificial Intelligence} (AAAI), February 2020. (Acceptance rate 20.6\% = 1591/7737)

\item[C34] Yao, H., Zhang, C., Wei, Y., \textbf{Jiang, M.}, Wang, S., Chawla, N.V., Li, Z. ``Graph Few-shot Learning via Knowledge Transfer'', in Proceedings of \textit{AAAI Conference on Artificial Intelligence} (AAAI), February 2020. (Acceptance rate 20.6\% = 1591/7737)

\item[C33] @Ding, Y., @Wang, D., Weninger, T., \textbf{Jiang, M.} ``Preserving Composition and Crystal Structure Information of Chemical Compounds in Atomic Embedding'', in Proceedings of \textit{IEEE International Conference on Big Data} (BigData), December 2019. (Poster)

\item[C32] @Jiang, T., *Zhang, Z., @Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``CTGA: Graph-based Biomedical Literature Search'', in Proceedings of \textit{IEEE International Conference on Bioinformatics and Biomedicine} (BIBM), November 2019. (Acceptance rate 18\% = 98/543)

\item[C31] @Jiang, T., @Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``Multi-input Multi-output Sequence Labeling for Joint Extraction of Fact and Condition Tuples from Scientific Text'' in Proceedings of \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), November 2019. (Acceptance rate 23\% = 465/2022)

\item[C30] Wang, T., Xu, X., Xiong, J., \textbf{Jiang, M.}, Shi, Y. ``MSU-Net: Multiscale Statistical U-Net for Real-time 3D Cardiac MRI Video Segmentation'' in Proceedings of \textit{International Conference on Medical Image Computing and Computer Assisted Intervention} (MICCAI), October 2019. (Acceptance rate 31\% = 536/1729)

\item[C29] @Jiang, T., @Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``The Role of Condition: A Novel Scientific Knowledge Graph Representation and Construction Model'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2019. (Acceptance rate 14.2\% = 170/1200)

\item[C28] @Wang, D., @Jiang, T., Chawla, N.V., \textbf{Jiang, M.} ``TUBE: Embedding Behavior Outcomes for Predicting Success'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2019. (Acceptance rate 9.2\% = 110/1200; selected for \textbf{Best Paper Award} at the Annual Meeting of the International Society for Data Science and Analytics)
	
\item[C27] *Yu, W., Li, Z., @Zeng, Q., \textbf{Jiang, M.} ``Tablepedia: Automating PDF Table Reading in an Experimental Evidence Exploration and Analytic System'' in Proceedings of \textit{The Web Conference} (TheWebConf), May 2019. (Demo)
	
\item[C26] @Wang, X., @Zhang, H., @Li, Q., Shi, Y., \textbf{Jiang, M.} ``A Novel Unsupervised Approach for Precise Temporal Slot Filling from Incomplete and Noisy Temporal Contexts'' in Proceedings of \textit{The Web Conference} (TheWebConf), May 2019. (Acceptance rate 18.0\% = 225/1247; selected for \textbf{Best Poster Award} at the 13th Annual Poster Contest at ND CSE)

\item[C25] @Zhao, T., *Malir, M., \textbf{Jiang, M.} ``Actionable Objective Optimization for Suspicious Behavior Detection on Large Bipartite Graphs'' in Proceedings of \textit{IEEE International Conference on Big Data} (BigData), December 2018. (Acceptance rate 18.9\% = 98/518)

\item[C24] Tao, F., Zhang, C., Chen, X., \textbf{Jiang, M.}, Hanratty, T., Kaplan, L., Han, J. ``Doc2Cube: Allocating Documents to Text Cube without Labeled Data'' in Proceedings of \textit{IEEE International Conference on Data Mining} (ICDM), November 2018. (Acceptance rate 11.1\% = 105/948)

\item[C23] Ding, Y., Liu, J., Xiong, J., \textbf{Jiang, M.}, Shi, Y. ``Optimizing Boiler Control in Real-Time with Machine Learning for Sustainability'' in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2018. (Acceptance rate 26.0\% = 34/130)

\item[C22] Zhao, S., \textbf{Jiang, M.}, Liu, M., Qin, B., Liu, T. ``CausalTriad: Toward Pseudo Causal Relation Discovery and Hypotheses Generation from Medical Text Data'' in Proceedings of \textit{ACM International Conference on Bioinformatics, Computational Biology, and Health Informatics} (BCB), August 2018. (Acceptance rate 31.1\% = 46/148)

\item[C21] @Wang, D., \textbf{Jiang, M.}, @Wang, X., @Zhao, T., @Zeng, Q., Chawla, N.V. ``A Project Showcase for Planning Research Work towards Publishable Success'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2018. (Demo)

\item[C20] Zhang, C., Tao, F., Chen, X., Shen, J., \textbf{Jiang, M.}, Sadler, B., Vanni, M., Han, J. ``TaxoGen: Constructing Topical Concept Taxonomy by Adaptive Term Embedding and Clustering'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2018. (Acceptance rate 10.9\% = 107/983)

\item[C19] \textbf{Jiang, M.}, Li, Q., Zhang, X., Qu, M., Hanratty, T., Gao, J., Han, J. ``TruePIE: Discovering Reliable Patterns in Pattern-Based Information Extraction'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2018. (Acceptance rate 10.9\% = 107/983)
	
\item[C18] @Wang, D., \textbf{Jiang, M.}, @Zeng, Q., @Eberhart, Z., Chawla, N.V. ``Multi-Type Itemset Embedding for Learning Behavior Success'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2018. (Acceptance rate 10.9\% = 107/983)

\item[C17] Zhao, S., \textbf{Jiang, M.}, Yuan, Q., Qin, B., Liu, T., Zhai, C.X. ``ContextCare: Incorporating Contextual Information Networks to Representation Learning in Medical Forum Data'' in Proceedings of \textit{International Joint Conference on Artificial Intelligence} (IJCAI), August 2017. (Acceptance rate 26.0\% = 660/2540)

\item[C16] \textbf{Jiang, M.}, Shang, J., Cassidy, T., Ren, X., Kaplan, L., Hanratty, T., Han, J. ``MetaPAD: Meta Patten Discovery from Massive Text Corpora'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2017. (Acceptance rate 13.7\% = 130/748)

\item[C15] Kuang, K., Cui, P., Li, B., \textbf{Jiang, M.}, Yang, S., Wang, F. ``Estimating Treatment Effect in the Wild via Differentiated Confounder Balancing'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2017. (Acceptance rate 13.7\% = 130/748)

\item[C14] Ren, X., Shen, J., Qu, M., Wang, X., Wu, Z., Zhu, Q., \textbf{Jiang, M.}, Tao, F., Sinha, S., Liem, D., Ping, P., Weinshilboum, R., Han, J. ``LifeNet: A Structured Network-Based Knowledge Exploration and Analytics System for Life Sciences'' in Proceedings of \textit{Annual Meeting of the Association for Computational Linguistics} (ACL), July 2017. (Demo)

\item[C13] Kuang, K., Cui, P., Li, B., \textbf{Jiang, M.}, Yang, S., Wang, F. ``Treatment Effect Estimation with Data-Driven Variable Decomposition'' in Proceedings of \textit{AAAI Conference on Artificial Intelligence} (AAAI), February 2017. (Acceptance rate 24.6\% = 638/2590)

\item[C12] Kuang, K., \textbf{Jiang, M.}, Cui, P., Yang, S. ``Steering Social Media Promotions with Effective Strategies'' in Proceedings of \textit{IEEE International Conference on Data Mining} (ICDM), November 2016. (Acceptance rate 19.6\% = 177/904)

\item[C11] Gui, H., Liu, J., Tao, F., \textbf{Jiang, M.}, Norick, B., Han, J. ``Large-Scale Embedding Learning in Heterogeneous Event Data'' in Proceedings of \textit{IEEE International Conference on Data Mining} (ICDM), November 2016. (Acceptance rate 19.6\% = 177/904)

\item[C10] \textbf{Jiang, M.}, Faloutsos, C., Han, J. ``CatchTartan: Representing and Summarizing Dynamic Multicontextual Behaviors'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2016. (Acceptance rate 8.9\% = 70/784)

\item[C9] \textbf{Jiang, M.}, Cui, P., Yuan, N.J., Xie, X., Yang, S. ``Little is Much: Bridging Cross-Platform Behaviors through Overlapped Crowds'' in Proceedings of \textit{AAAI Conference on Artificial Intelligence} (AAAI), February 2016. (Acceptance rate 25.8\% = 550/2132)

\item[C8] \textbf{Jiang, M.}, Beutel, A., Cui, P., Hooi, B., Yang, S., Faloutsos, C. ``A General Suspiciousness Metric for Dense Blocks in Multimodal Data'' in Proceedings of \textit{IEEE International Conference on Data Mining} (ICDM), November 2015. (Acceptance rate 18.1\% = 146/807)

\item[C7] \textbf{Jiang, M.}, Cui, P., Wang, F., Xu, X., Zhu, W., Yang, S. ``FEMA: Flexible Evolutionary Multi-Faceted Analysis for Dynamic Behavioral Pattern Discovery'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2014. (Acceptance rate 14.6\% = 151/1036)

\item[C6] \textbf{Jiang, M.}, Cui, P., Beutel, A., Faloutsos, C., Yang, S. ``CatchSync: Catching Synchronized Behavior in Large Directed Graphs'' in Proceedings of \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2014. (Acceptance rate 14.6\% = 151/1036; selected as \textbf{best paper finalist} and invited to TKDD special issue)
	
\item[C5] \textbf{Jiang, M.}, Cui, P., Beutel, A., Faloutsos, C., Yang, S. ``Inferring Strange Behavior from Connectivity Pattern in Social Networks'' in Proceedings of \textit{Pacific-Asia Conference on Knowledge Discovery and Data Mining} (PAKDD), April 2014. (Acceptance rate 10.8\% = 40/371)

\item[C4] \textbf{Jiang, M.}, Cui, P., Beutel, A., Faloutsos, C., Yang, S. ``Detecting Suspicious Following Behavior in Multimillion-Node Social Networks'' in Proceedings of \textit{International Conference on World Wide Web} (WWW), April 2014. (Poster)

\item[C3] \textbf{Jiang, M.}, Cui, P., Wang, F., Yang, Q., Zhu, W., Yang, S. ``Social Recommendation across Multiple Relational Domains'' in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2012. (Acceptance rate 13.4\% = 146/1088)

\item[C2] \textbf{Jiang, M.}, Cui, P., Liu, R., Yang, Q., Wang, F., Zhu, W., Yang, S. ``Social Contextual Recommendation'' in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2012. (Acceptance rate 13.4\% = 146/1088)

\item[C1] Liu, L., Tang, J., Han, J., \textbf{Jiang, M.}, Yang, S. ``Mining Topic-Level Influence in Heterogeneous Networks'' in Proceedings of \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2010. (Acceptance rate 13.3\% = 126/945)

\end{enumerate}

\hspace{-0.25cm}\textit{Journal Papers} {\small (8 IEEE Trans. on Knowledge \& Data Eng. (TKDE), etc.)}

\begin{enumerate}[leftmargin=.5cm]

\item[J31] @Wang, D., @Zhao, T., @Yu, W., Chawla, N.V., \textbf{Jiang, M.} ``Deep Multimodal Complementarity Learning'', \textit{IEEE Transactions on Neural Networks and Learning Systems}. Early Access. 1-12, April 2022. (IF=8.793; DOI: 10.1109/TNNLS.2022.3165180)

\item[J30] Gu, S., \textbf{Jiang, M.}, Guzzi, P.H., Milenkovic, T. ``Modeling Multi-scale Data via a Network of Networks'', \textit{Bioinformatics}. Early Access. btac133, March 2022. (IF=6.937; DOI: 10.1093/bioinformatics/btac133)

\item[J29] @Yu, W., Zhu, C., *Li, Z., Hu, Z., Wang, Q., Ji, H., \textbf{Jiang, M.} ``A Survey of Knowledge-Enhanced Text Generation'', \textit{ACM Computing Surveys}. Early Access. March 2022. (IF=10.28; DOI: 10.1145/3512467)

\item[J28] \textbf{Jiang, M.}, Jung, T., Karl, R., @Zhao, T. ``Federated Dynamic Graph Neural Networks with Secure Aggregation for Video-based Distributed Surveillance'', \textit{ACM Transactions on Intelligent Systems and Technology}. Early Access. February 2022. (IF=2.861; DOI: 10.1145/3501808)

\item[J27] *Chou, D., \textbf{Jiang, M.} ``A Survey on Data-Driven Network Intrusion Detection'', \textit{ACM Computing Surveys}. 54:9, 1-36, December 2022. (IF=10.28; DOI: 10.1145/3472753)

\item[J26] @Zhao, T., @Jiang, T., Shah, N., \textbf{Jiang, M.} ``A Synergistic Approach for Graph Anomaly Detection with Pattern Mining and Feature Learning'', \textit{IEEE Transactions on Neural Networks and Learning Systems}. Early Access. 1-13, August 2021. (IF=8.793; DOI: 10.1109/TNNLS.2021.3102609)

\item[J25] @Wang, D., *Zhang, Z., *Ma, Y., @Zhao, T., @Jiang, T., Chawla, N.V., \textbf{Jiang, M.} ``Modeling Co-evolution of Attributed and Structural Information in Graph Sequence'', \textit{IEEE Transactions on Knowledge and Data Engineering}. Early access. 1-1, July 2021. (IF=6.977; DOI: 10.1109/TKDE.2021.3094332)

\item[J24] Zhao, S., \textbf{Jiang, M.}, Qin, B., Liu, T., Zhai, C.X., Wang, F. ``Structural and Textual Information Fusion for Symptom and Disease Representation Learning'', \textit{IEEE Transactions on Knowledge and Data Engineering}. Early access. 1-1, November 2020. (IF=6.977; DOI: 10.1109/TKDE.2020.3039469)

\item[J23] Syed, M., @Wang, D., \textbf{Jiang, M.}, Conway, O., Juneja, V., Subramanian, S., Chawla, N.V. ``Unified Representation of Twitter and Online News using Graph and Entities'', \textit{Frontiers in Big Data, section Big Data Networks}. 4:699070, August 2021. (IF=[new journal]; DOI: 10.3389/fdata.2021.699070)

\item[J22] @Wang, D., @Zeng, Q., Chawla, N.V., \textbf{Jiang, M.} ``Modeling Complementarity in Behavior Data with Multi-Type Itemset Embedding'', \textit{ACM Transactions on Intelligent Systems and Technology}. 12:4, 1-25, August 2021. (IF=2.861; DOI: 10.1145/3458724)

\item[J21] @Jiang, T., @Zeng, Q., @Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``Biomedical Knowledge Graphs Construction from Conditional Statements'' \textit{IEEE/ACM Transactions on Computational Biology and Bioinformatics}. 18:3, 823-835, May-June 2021. (IF=3.015; DOI: 10.1109/TCBB.2020.2979959)

\item[J20] Zhang, C., Yao, H., Yu, L., Huang, C., Song, D., \textbf{Jiang, M.}, Chen, H., Chawla, N.V. ``Inductive Contextual Relation Learning for Personalization'', \textit{ACM Transactions on Information Systems}. 39:3, 1-22, May 2021. (IF=2.312; DOI: 10.1145/3450353)

\item[J19] Liu, J., Xu, X., \textbf{Jiang, M.}, Shi, Y. ``Binarizing Weights Wisely for Edge Intelligence: Guide for Partial Binarization of Deconvolution-Based Generators'' \textit{IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems}. 39:12, 4748-4759, December 2020. (IF=2.168; DOI: 10.1109/TCAD.2020.2983370)

\item[J18] Liu, Z., \textbf{Jiang, M.}, Luo, T. ``Leverage Electron Properties to Predict Phonon Properties via Transfer Learning for Semiconductors'' \textit{Science Advances}. 6:45, eabd1356, November 2020. (IF=12.530; DOI: 10.1126/sciadv.abd1356)
	
\item[J17] Zhou, S., Hu, Z., Gu, W., \textbf{Jiang, M.}, Chen, M., Hong, Q., Booth, C. ``Combined Heat and Power System Intelligent Economic Dispatch: A Deep Reinforcement Learning Approach'' \textit{International Journal of Electrical Power and Energy Systems}. 120, September 2020. (IF=3.588; DOI: 10.1016/j.ijepes.2020.106016)

\item[J16] @Wang, X., \textbf{Jiang, M.} ``Precise Temporal Slot Filling via Truth Finding with Data-Driven Commonsense'' \textit{Knowledge and Information Systems}. 1-27, July 2020. (IF=2.936; DOI: 10.1007/s10115-020-01493-w)

\item[J15] \textbf{Jiang, M.}, Ammerman, B.A., @Zeng, Q., Jacobucci, R., Brodersen, A. ``Phrase-level Pairwise Topic Modeling to Uncover Helpful Peer Responses to Online Suicidal Crises'' \textit{Humanities \& Social Sciences Communications} (formerly known as \textit{Nature Palgrave Communications}). 7:36, July 2020. (IF=[new journal]; DOI: 10.1057/s41599-020-0513-5)

\item[J14] Kuang, K., Cui, P., Li, B., \textbf{Jiang, M.}, Yang, S. ``Treatment Effect Estimation via Differentiated Confounder Balancing and Regression'' \textit{ACM Transactions on Knowledge Discovery from Data}. 14:1, 1-25, December 2019. (IF=2.200; DOI: 10.1145/3365677)
	
\item[J13] Zhou, S., Hu, Z., Zhong, Z., He, D., \textbf{Jiang, M.} ``An Integrated Energy System Operating Scenarios Generator based on Generative Adversarial Network'' \textit{Sustainability}. 11:23, 6699, November 2019. (IF=2.576; DOI: 10.3390/su11236699)

\item[J12] Zhou, S., Hu, Z., Gu, W., \textbf{Jiang, M.}, Zhang, X.P. ``Artificial Intelligence based Smart Energy Community Management: A Reinforcement Learning Approach'' \textit{CSEE Journal of Power and Energy Systems}. 5:1, 1-10, March 2019. (IF=2.680; DOI: 10.17775/CSEEJPES.2018.00840)

\item[J11] Kuang, K., \textbf{Jiang, M.}, Cui, P., Luo, H., Yang, S. ``Effective Promotional Strategies Selection in Social Media: A Data-Driven Approach'' \textit{IEEE Transactions on Big Data}. 4:4, 487-501, December 2018. (IF=3.344; DOI: 10.1109/TBDATA.2017.2734102)

\item[J10] Shang, J., Liu, J., \textbf{Jiang, M.}, Ren, X., Voss, C.R., Han, J. ``Automated Phrase Mining from Massive Text Corpora'' \textit{IEEE Transactions on Knowledge and Data Engineering}. 30:10, 1825-1837, October 2018. (IF=6.977; DOI: 10.1109/TKDE.2018.2812203)

\item[J9] Shang, J., \textbf{Jiang, M.}, Tong, W., Xiao, J., Peng, J., Han, J. ``DPPred: An Effective Prediction Framework with Concise Discriminative Patterns'' \textit{IEEE Transactions on Knowledge and Data Engineering}. 30:7, 1226-1239, July 2018. (IF=6.977; DOI: 10.1109/TKDE.2017.2757476)

\item[J8] Gui, H., Liu, J., Tao, F., \textbf{Jiang, M.}, Norick, B., Kaplan, L., Han, J. ``Embedding Learning with Events in Heterogeneous Information Networks'' \textit{IEEE Transactions on Knowledge and Data Engineering}. 29:11, 2428-2441, July 2017. (IF=6.977; DOI: 10.1109/TKDE.2017.2733530)

\item[J7] \textbf{Jiang, M.}, Cui, P., Beutel, A., Faloutsos, C., Yang, S. ``Inferring Lockstep Behavior from Connectivity Pattern in Large Graphs'' \textit{Knowledge and Information Systems}. 48:2, 399-428, August 2016. (IF=2.822; DOI: 10.1007/s10115-015-0883-y)

\item[J6] \textbf{Jiang, M.}, Cui, P., Beutel, A., Faloutsos, C., Yang, S. ``Catching Synchronized Behaviors in Large Networks: A Graph Mining Approach'' \textit{ACM Transactions on Knowledge Discovery from Data - Special Issue on SIGKDD 2014}. 10:4, 35:1-35:27, July 2016. (IF=4.54; DOI: 10.1109/MIS.2016.5)

\item[J5] \textbf{Jiang, M.}, Beutel, A., Cui, P., Hooi, B., Yang, S., Faloutsos, C. ``Spotting Suspicious Behaviors in Multimodal Data: A General Metric and Algorithms'' \textit{IEEE Transactions on Knowledge and Data Engineering}. 28:8, 2187-2200, April 2016. (IF=6.977; DOI: 10.1109/TKDE.2016.2555310)

\item[J4] \textbf{Jiang, M.}, Cui, P., Yang, S. ``Suspicious Behavior Detection: Current Trends and Future Directions'' \textit{IEEE Intelligent Systems}. 31:1, 31-39, January 2016. (IF=2.596; DOI: 10.1109/MIS.2016.5)

\item[J3] \textbf{Jiang, M.}, Cui, P., Chen, X., Wang, F., Zhu, W., Yang, S. ``Social Recommendation with Cross-Domain Transferable Knowledge'' \textit{IEEE Transactions on Knowledge and Data Engineering}. 27:11, 3084-3097, November 2015. (IF=6.977; DOI: 10.1109/TKDE.2015.2432811)

\item[J2] \textbf{Jiang, M.}, Cui, P., Wang, F., Zhu, W., Yang, S. ``Scalable Recommendation with Social Contextual Information'' \textit{IEEE Transactions on Knowledge and Data Engineering}. 26:11, 2789-2802, November 2014. (IF=6.977; DOI: 10.1109/TKDE.2014.2300487)

\item[J1] Liu, L., Zhu, F., \textbf{Jiang, M.}, Han, J., Sun, L., Yang, S. ``Mining Diversity on Social Media Networks'' \textit{Multimedia Tools and Applications}. 56:1, 179-205, January 2012. (IF=2.313; DOI: 10.1007/s11042-010-0568-1)

\end{enumerate}

\hspace{-0.25cm}\textit{Workshop Papers}

\begin{enumerate}[leftmargin=.5cm]

\item[W15] @Zeng, Q., @Yu, M., @Yu, W., @Jiang, T., \textbf{Jiang, M.} ``Validating Label Consistency in NER Data Annotation'', in the \textit{Workshop on Evaluation and Comparison of NLP Systems} (Eval4NLP) in conjunction with \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), 2021.

\item[W14] @Wang, D., @Zhao, T., Chawla, N.V., \textbf{Jiang, M.} ``Evolutionary Graph Normalizing Flows'', in the \textit{International Workshop on Deep Learning on Graphs: Methods and Applications} (DLG) in conjunction with \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2021.

\item[W13] *Alaphat, A., \textbf{Jiang, M.} ``SmartFund: Predicting Research Outcomes with Machine Learning and Natural Language Processing'', in the \textit{International Workshop on Big Data Tools, Methods, and Use Cases for Innovative Scientific Discovery} (BTSD) in conjunction with \textit{IEEE International Conference on Big Data} (BigData), 2020. (Regular paper, 10 pages. The first author was a freshman undergraduate when he finished the work. He won \$250 grant funding from the CUSE program.)

\item[W12] @Wang, D., *Zhang, Z., *Ma, Y., @Zhao, T., @Jiang, T., Chawla, N.V., \textbf{Jiang, M.} ``Learning Attribute-Structure Co-Evolutions in Dynamic Graphs'', in the \textit{Second International Workshop on Deep Learning on Graphs: Methods and Applications} (DLG) in conjunction with \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2020. (selected for \textbf{Best Paper Award})

\item[W11] @Zhao, T., *Ni, B., @Yu, W., \textbf{Jiang, M.} ``Early Fraud Detection with Augmented Graph Learning'', in the \textit{Second International Workshop on Deep Learning on Graphs: Methods and Applications} (DLG) in conjunction with \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2020.

\item[W10] @Zhao, T., *Deng, C., *Yu, K., @Jiang, T., @Wang, D., \textbf{Jiang, M.} ``GNN-based Graph Anomaly Detection with Graph Anomaly Loss'', in the \textit{Second International Workshop on Deep Learning on Graphs: Methods and Applications} (DLG) in conjunction with \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2020.

\item[W9] *Zhou, Y., @Zhao, T., \textbf{Jiang, M.} ``A Probabilistic Model with Commonsense Constraints for Pattern-based Temporal Fact Extraction'', in the \textit{Workshop on Fact Extraction and Verification} (FEVER) in conjunction with \textit{Annual Meeting of the Association for Computational Linguistics} (ACL), July 2020.

\item[W8] @Yu, W., Wu, L., Tao, S., Deng, Y., @Zeng, Q., \textbf{Jiang, M.} ``Generating Helpful Responses for Intelligent Tech Support'', in the \textit{Reasoning for Complex QA  Workshop} (RCQA) in conjunction with \textit{AAAI Conference on Artificial Intelligence} (AAAI), February 2020.

\item[W7] Yao, H., Zhang, C., Wei, Y., \textbf{Jiang, M.}, Wang, S., Chawla, N.V., Li, Z. ``Graph Few-shot Learning via Knowledge Transfer'', in the \textit{Graph Representation Learning Workshop} (GRL) in conjunction with \textit{Conference on Neural Information Processing Systems} (NeurIPS), November 2019.
	
\item[W6] @Zeng, Q., *Yu, M., @Yu, W., Xiong, J., Shi, Y., \textbf{Jiang, M.} ``Faceted Hierarchy: A New Graph Type to Organize Scientific Concepts and a Construction Method'', in the \textit{Workshop on Graph-Based Natural Language Processing} (TextGraphs) in conjunction with \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), November 2019.

\item[W5] *Ma, Y., @Zeng, Q., @Jiang, T., Cai, L., \textbf{Jiang, M.} ``A Study of Person Entity Extraction and Profiling from Classical Chinese Historiography'', in the \textit{International Workshop on EntitY REtrieval} (EYRE) in conjunction with \textit{ACM International Conference on Information and Knowledge Management} (CIKM), November 2019.

\item[W4] @Jiang, T., @Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``Constructing Information-Lossless Biological Knowledge Graphs from Conditional Statements'' in the 18th \textit{International Workshop on Data Mining in Bioinformatics} (BIOKDD) in conjunction with \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2019.

\item[W3] @Wang, D., \textbf{Jiang, M.}, @Wang, X., Chawla, N.V., Brunts, P. ``Multifaceted Event Analysis on Cross-Media Network Data'' in the \textit{International Workshop on Heterogeneous Networks Analysis and Mining} (HeteroNAM) in conjunction with \textit{ACM Conference on Web Search and Data Mining} (WSDM), February 2018.

\item[W2] Chen, L.W., Mangipudi, B., Bandlamudi, J., Sehgal, R., Hao, Y., \textbf{Jiang, M.} ``Integrating Knowledge from Latent and Explicit Features for Triple Scoring—Team Radicchio's Triple Scorer at WSDM Cup 2017'' in the 10th \textit{ACM Conference on Web Search and Data Mining Notebook Papers} (WSDM), February 2017.

\item[W1] \textbf{Jiang, M.} ``Catching Social Media Advertisers with Strategy Analysis'' in the 1st \textit{International Workshop on Computational Methods for CyberSafety} in conjunction with \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2016.

\end{enumerate}

\hspace{-0.25cm}\textit{Refereed Conference Tutorials}

\begin{enumerate}[leftmargin=.5cm]

\item[T12] Zhu, C., Xu, Y., \textbf{Jiang, M.}, @Yu, W., Ren, X., Lin, Y. ``Knowledge-Augmented Methods for Natural Language Processing'' in the \textit{Annual Meeting of the Association for Computational Linguistics} (ACL), May 2022.

\item[T11] @Yu, W., \textbf{Jiang, M.}, Hu, Z., Wang, Q., Ji, H., Rajani, N. ``Knowledge-Enriched Natural Language Generation'', in the \textit{Conference on Empirical Methods in Natural Language Processing} (EMNLP), November 2021.

\item[T10] Zhang, C., Li, J., \textbf{Jiang, M.} ``Data Efficient Learning on Graphs'', in the \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2021.
		
\item[T9] \textbf{Jiang, M.}, Shang, J. ``Scientific Text Mining and Knowledge Graphs'' in the \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2020.
		
\item[T8] Zhang, C., \textbf{Jiang, M.}, Zhang, X., Ye, Y., Chawla, N.V. ``Multi-modal Network Representation Learning: Methods and Applications'' in the \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2020.

\item[T7] Zhang, C., \textbf{Jiang, M.}, Zhang, X., Chawla, N.V. ``Multi-modal Network Representation Learning: Methods and Applications'' in the \textit{SIAM International Conference on Data Mining} (SDM), May 2020. (accepted but cancelled due to COVID-19)

\item[T6] \textbf{Jiang, M.}, Kumar, S., Subrahmanian, V.S., Faloutsos, C. ``Data-Driven Approaches towards Malicious Behavior Modeling'' in the \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2017.

\item[T5] Shang, J., \textbf{Jiang, M.}, Ren, X., Han, J. ``Mining Entity-Relation-Attribute Structures from Massive Text Data'' in the \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), August 2017.

\item[T4] Ren, X., \textbf{Jiang, M.}, Shang, J., Han, J. ``Building Structured Databases of Factual Knowledge from Massive Text Data'' in the \textit{ACM SIGMOD International Conference on Management of Data} (SIGMOD), May 2017.
		
\item[T3] Ren, X., \textbf{Jiang, M.}, Shang, J., Han, J. ``Constructing Structured Information Networks from Massive Text Corpora'' in the \textit{International World Wide Web Conference}  (WWW), April 2017.

\item[T2] \textbf{Jiang, M.}, Cui, P., Han, J. ``Data-Driven Behavioral Analytics: Observations, Representations and Models'' in the \textit{ACM International Conference on Information and Knowledge Management} (CIKM), October 2016.
		
\item[T1] \textbf{Jiang, M.}, Cui, P. ``Behavior Modeling in Social Networks: From Micro to Macro'' in the \textit{IEEE International Conference on Data Mining} (ICDM), November 2015.

\end{enumerate}

\hspace{-0.25cm}\textit{Invited Book Chapters}

\begin{enumerate}[leftmargin=.5cm]

\item[BC3] \textbf{Jiang, M.}, Zhang, C., Zhang, X., Shah, N. ``Editorial: Computational Behavioral Modeling for Big User Data'' Frontiers in Big Data, section Big Data Networks, 2022.
		
\item[BC2] \textbf{Jiang, M}. ``Behavior Modeling in Social Networks'' Encyclopedia of Social Network Analysis and Mining, Springer, New York, NY, 2017.
		
\item[BC1] \textbf{Jiang, M.}, Cui, P. ``Mining User Behaviors in Large Social Networks'' Chapter 4, Big Data in Complex and Social Networks, Chapman \& Hall/CRC Big Data Series, 2016.

\end{enumerate}

\hide{
\hspace{-0.25cm}\textit{Preprints}

\begin{enumerate}[leftmargin=.5cm]

\item[P32] @Yu, W., Zhu, C., Qin, L., @Zhao, T. \textbf{Jiang, M.} ``Diversifying Content Generation for Commonsense Reasoning with Mixture of Knowledge Graph Experts'', in \textit{arXiv preprint arXiv:2203.07285}, March 2022. (accepted in ACL 2022)

\item[P31] @Zhao, T., @Liu, G., Günnemann, S., \textbf{Jiang, M.} ``Graph Data Augmentation for Graph Machine Learning: A Survey'', in \textit{arXiv preprint arXiv:2202.08871}, February 2022.
		
\item[P30] *Kuebler, J., @Tong, L., \textbf{Jiang, M.} ``Multi-Round Parsing-based Multiword Rules for Scientific OpenIE'', in \textit{arXiv preprint arXiv:2108.02074}, August 2021. (accepted in ICBK 2021)

\item[P29] @Zeng, Q., Lin, J., Yu, W., Cleland-Huang, J., \textbf{Jiang, M.} ``Enhancing Taxonomy Completion with Concept Generation via Fusing Relational Representations'', in \textit{arXiv preprint arXiv:2106.02974}, June 2021. (accepted in KDD 2021)

\item[P28] @Zhao, T., @Liu, G., @Wang, D., @Yu, W., \textbf{Jiang, M.} ``Counterfactual Graph Learning for Link Prediction'', in \textit{arXiv preprint arXiv:2106.02172}, June 2021.

\item[P27] \textbf{Jiang, M.} ``Cross-Network Learning with Partially Aligned Graph Convolutional Networks'', in \textit{arXiv preprint arXiv:2106.01583}, June 2021. (accepted in KDD 2021)

\item[P26] Gu, S., \textbf{Jiang, M.}, Guzzi, P.H., Milenkovic, T. ``Modeling Multi-scale Data via a Network of Networks'', in \textit{arXiv preprint arXiv:2105.12226}, May 2021. (accepted in Bioinformatics)

\item[P25] @Yu, W., Zhu, C., @Zhao, T., Guo, Z., \textbf{Jiang, M.} ``Sentence-Permuted Paragraph Generation'', in \textit{arXiv preprint arXiv:2104.07228}, April 2021. (accepted in EMNLP 2021)

\item[P24] @Wang, D., Shiralkar, P., Lockard, C., Huang, B., Dong, X.L., \textbf{Jiang, M.} ``TCN: Table Convolutional Network for Web Table Interpretation'', in \textit{arXiv preprint arXiv:2102.09460}, February 2021. (accepted in TheWebConf 2021)

\item[P23] Guo, Z., Zhang, C., @Yu, W., Herr, J., Wiest, O., \textbf{Jiang, M.}, Chawla, N.V. ``Few-Shot Graph Learning for Molecular Property Prediction'', in \textit{arXiv preprint arXiv:2102.07916}, February 2021. (accepted in TheWebConf 2021)

\item[P22] @Zeng, Q., @Yu, M., @Yu, W., Jiang, T., Weninger, T., \textbf{Jiang, M.} ``Validating Label Consistency in NER Data Annotation'', in \textit{arXiv preprint arXiv:2101.08698}, January 2021. (accepted in Eval4NLP 2021)

\item[P21] @Zhao, T., *Ni, B., @Yu, W., Guo, Z., Shah, N., \textbf{Jiang, M.} ``Action Sequence Augmentation for Early Graph-based Anomaly Detection'', in \textit{arXiv preprint arXiv:2010.10016}, October 2020. (accepted in CIKM 2021)

\item[P20] @Yu, W., Wu, L., @Zeng, Q., Deng, Y., Mahindru, R., Guven, S., \textbf{Jiang, M.} ``Technical Question Answering across Tasks and Domains'', in \textit{arXiv preprint arXiv:2010.09780}, October 2020. (accepted in NAACL 2021)

\item[P19] @Yu, W., Zhu, C., *Li, Z., Hu, Z., Wang, Q., Ji, H., \textbf{Jiang, M.} ``A Survey of Knowledge-Enhanced Text Generation'', in \textit{arXiv preprint arXiv:2010.04389}, October 2020. (accepted in ACM Computing Surveys)
		
\item[P18] *Dong, X., @Yu, W., Zhu, C., \textbf{Jiang, M.} ``Injecting Entity Types into Entity-Guided News Generation'', in \textit{arXiv preprint arXiv:2009.13401}, September 2020. (accepted in EMNLP 2021)
		
\item[P17] *Chou, D., \textbf{Jiang, M.} ``Data-Driven Network Intrusion Detection: A Taxonomy of Challenges and Methods'', in \textit{arXiv preprint arXiv:2009.07352}, September 2020. (accepted in ACM Computing Surveys)

\item[P16] \textbf{Jiang, M.}, Jung, T., Karl, R., @Zhao, T. ``Federated Dynamic GNN with Secure Aggregation'', in \textit{arXiv preprint arXiv:2009.07351}, September 2020. (accepted in ACM TIST)

\item[P15] Liu, Z., \textbf{Jiang, M.}, Lin, H. ``Specification Mining and Automated Task Planning for Autonomous Robots based on a Graph-based Spatial Temporal Logic'' in \textit{arXiv preprint arXiv:2007.08451}, July 2020.

\item[P14] @Jiang, T., @Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``Canonicalizing Open Knowledge Bases with Multi-Layered Meta-Graph Neural Network'' in \textit{arXiv preprint arXiv:2006.09610}, June 2020.
		
\item[P13] @Zhao, T., Liu, Y., Neves, L., Woodford, O., \textbf{Jiang, M.}, Shah, N. ``Data Augmentation for Graph Neural Networks'' in \textit{arXiv preprint arXiv:2006.06830}, June 2020. (accepted in AAAI 2021)

\item[P12] @Wang, D., \textbf{Jiang, M.}, Syed, M., Conway, O., Juneja, V., Subramanian, S., Chawla, N.V. ``Calendar Graph Neural Networks for Modeling Time Structures in Spatiotemporal User Behaviors'' in \textit{arXiv preprint arXiv:2006.06820}, June 2020. (accepted in KDD 2020)
		
\item[P11] *Zhou, Y., @Zhao, T., \textbf{Jiang, M.} ``A Probabilistic Model with Commonsense Constraints for Pattern-based Temporal Fact Extraction'' in \textit{arXiv preprint arXiv:2006.06436}, June 2020. (accepted in ACL-FEVER 2020)

\item[P10] @Yu., W., Wu., L., @Zeng, Q., Deng, Yu, Tao, S., \textbf{Jiang, M.} ``Crossing Variational Autoencoders for Answer Retrieval'' in \textit{arXiv preprint arXiv:2005.02557}, May 2020. (accepted in ACL 2020)
		
\item[P9] Zhu, C., Hinthorn, W., Xu, R., Zeng, @Q., Zeng, M., Huang, X., \textbf{Jiang, M.} ``Boosting Factual Correctness of Abstractive Summarization with Knowledge Graph'' in \textit{arXiv preprint arXiv:2003.08612}, March 2020. (accepted in NAACL-HLT 2021)

\item[P8] Saebi, M., Krieg, S., Zhang, C., \textbf{Jiang, M.}, Chawla, N.V. ``Heterogeneous Relational Reasoning in Knowledge Graphs with Reinforcement Learning'' in \textit{arXiv preprint arXiv:2003.06050}, March 2020. (won the \textbf{first place} in ACM Student Research Competition -- Graduate Winners)

\item[P7] *Ni, B., @Guo, Z., @Li, J., \textbf{Jiang, M.} ``Improving Generalizability of Fake News Detection Methods using Propensity Score Matching'' in \textit{arXiv preprint arXiv:2002.00838}, January 2020.
		
\item[P6] Zhang, C., Yao, H., Huang, C., \textbf{Jiang, M.}, Li, Z., Chawla, N.V. ``Few-Shot Knowledge Graph Completion'' in \textit{arXiv preprint arXiv:1911.11298}, November 2019. (accepted in AAAI 2020)

\item[P5] Yao, H., Zhang, C., Wei, Y., \textbf{Jiang, M.}, Wang, S., Huang, J., Chawla, N.V., Li, Z. ``Graph Few-Shot Learning via Knowledge Transfer'' in \textit{arXiv preprint arXiv:1910.03053}, October 2019. (accepted in AAAI 2020)
		
\item[P4] Jiang, T., Zhao, T., Qin, B., Liu, T., Chawla, N.V., \textbf{Jiang, M.} ``Constructing Information-Lossless Biological Knowledge Graphs from Conditional Statements'' in \textit{arXiv preprint arXiv:1907.00720}, June 2019. (accepted in KDD 2019)
		
\item[P3] Liu, J., Zhang, J., Ding, Y., Xu, X., \textbf{Jiang, M.}, Shi, Y. ``PBGen: Partial Binarization of Deconvolution-Based Generators for Edge Intelligence'' in \textit{arXiv preprint arXiv:1802.09153}, February 2018. (accepted in TCADICS)
		
\item[P2] Shang, J., Shi, X., \textbf{Jiang, M.}, Liu, L., Hanratty, T., Han, J. ``Contrast Subgraph Mining from Coherent Cores'' in \textit{arXiv preprint arXiv:1802.06189}, February 2018.

\item[P1] \textbf{Jiang, M.}, Shang, J., Cassidy, T., Ren, X., Kaplan, L., Hanratty, T., Han, J. ``MetaPAD: Meta Patten Discovery from Massive Text Corpora'' in \textit{arXiv preprint arXiv:1703.04213 }, March 2017. (accepted in KDD 2017)

\end{enumerate}
}

\end{myindentpar}

\subsection{\sc Publications Under Review}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.00cm}

\vspace{.2cm}\hspace{-0.25cm}\textit{Conference Papers Under Review}

\begin{enumerate}[leftmargin=.5cm]

\item[CR4] @Zhao, T., Tang, X., Zhang, D., Rao, N., Song, Y., Agrawal, P., Subbian, K., Yin, B., \textbf{Jiang, M.} ``AutoGDA: Automated Graph Data Augmentation for Node Classification'', under review at \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2022.

\item[CR3] @Liu, G., @Zhao, T., Xu, J., Luo, T., \textbf{Jiang, M.} ``Graph Rationalization with Environment-based Augmentations'', under review at \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2022.

\item[CR2] @Hu, Z., \textbf{Jiang, M.} ``Solving Math Word Problems Automatically with Heterogeneous Line Graph Transformer for Online Learning'', under review at \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2022.

\item[CR1] Guo, X., @Zeng, Q., \textbf{Jiang, M.}, Yun, X., Long, B., Wu, L. ``Automatic Controllable Product Copywriting for E-Commerce'', under review at \textit{ACM SIGKDD International Conference on Knowledge Discovery and Data Mining} (KDD), 2022.

%\item[CR] @Zhao, T., @Liu, G., Günnemann, S., \textbf{Jiang, M.} ``Graph Data Augmentation for Graph Machine Learning: A Survey'', under review at \textit{} ().
	
%\item[CR] @Anuyah, O., @Douailly-Backman, J.-P., Metoyer, R., \textbf{Jiang, M.} ``Modeling User Behaviors to Predict Hatefulness Level of Posts on Gab'', under review at \textit{} ().

%\item[CR] Huang, C., Li, R., Zhang, C., \textbf{Jiang, M.}, Dai, P., Bo, L., Chawla, N.V. ``Multi-Grained Learning of Temporal Hierarchy for Time Series Forecasting'', under review at \textit{} ().

\end{enumerate}

\vspace{.2cm}\hspace{-0.25cm}\textit{Journal Papers Under Review}

\begin{enumerate}[leftmargin=.5cm]

\item[JR1] @Zhang, Z., @Yu, W., \textbf{Jiang, M.} ``Recent Advances of Multi-task Learning in NLP: Regarding Task Relatedness and Training Methods'', under review at \textit{IEEE Transactions on Audio, Speech, and Language Processing} (TASLP).

%\item[JR] Lu, Q., Jiang, W., \textbf{Jiang, M.}, Hu, J., Dasgupta, S., Shi, Y. ``Hardware/Software Co-Exploration for Graph Neural Architectures on FPGAs'', under review at \textit{Transactions on Computer-Aided Design of Integrated Circuits and Systems} (TCAD).

%\item[JR] Saebi, M., Krieg, S., Zhang, C., \textbf{Jiang, M.}, Kajdanowicz, T., Chawla, N.V. ``Heterogeneous Relational Reasoning in Knowledge Graphs with Reinforcement Learning'', under review at \textit{}.

%\item[JR] Syed, M., Krieg, S.J., Wang, D., \textbf{Jiang, M.}, Conway, O., Juneja, V., Subramanian, S., Chawla, N.V. ``Overcoming Data Sparsity and Class Imbalance with Graph Embeddings'', under review at \textit{Social Network Analysis and Mining}.

\end{enumerate}

%\vspace{.2cm}\hspace{-0.25cm}\textit{Patent Application Under Review}

%\begin{enumerate}[leftmargin=.5cm]

%\item[PR] @Yu, W., Wu, L., @Zeng, Q., Deng, Y., Mahindru, R., Guven, S., \textbf{Jiang, M.} ``Non-factoid Question Answering across Tasks and Domains'', P202100237US01.

%\end{enumerate}

%\vspace{.2cm}\hspace{-0.25cm}\textit{Refereed Workshop Papers}

%\begin{enumerate}[leftmargin=.5cm]

%\end{enumerate}

%\vspace{.2cm}\hspace{-0.25cm}\textit{Refereed Conference Tutorial}

%\begin{enumerate}[leftmargin=.5cm]

%\end{enumerate}

\end{myindentpar}

\subsection{\sc Invited Talks}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm} ICLR DLG Workshop Panel, Zoom, April 2022
	
\hspace{-0.75cm} Keynote speech at ACM WSDM MLoG Workshop, Zoom, February 2022
	
\hspace{-0.75cm} Keynote speech at IEEE/WIC/ACM WI-IAT Special Track on Social Computing, Zoom, December 2021

%\hspace{-0.75cm} Harbin Institute of Technology, Zoom, November 2021
	
\hspace{-0.75cm} Madison STEAM Academy (3rd, 4th, and 5th graders), South Bend, October 2021
	
\hspace{-0.75cm} NEC Laboratories Europe, Zoom, May 2021
	
\hspace{-0.75cm} Guest lecture in ``CSE 40625 Machine Learning'', Notre Dame, April 2021
	
\hspace{-0.75cm} Amazon Research, Zoom, November 2020

\hspace{-0.75cm} Guest lecture in ``CSE 40884 Network Science'', Notre Dame, October 2020

\hspace{-0.75cm} ACM SIGKDD TrueFacts Workshop Panel, Zoom, August 2020
	
\hspace{-0.75cm} Microsoft Research, Zoom, August 2020
	
\hspace{-0.75cm} Conference Follow-up from Artificial Intelligence and Machine Learning for Multi-Domain Operations, Zoom, May 2020
	
\hspace{-0.75cm} Saint Mary's College, Notre Dame, Indiana, February 2020
	
\hspace{-0.75cm} IBM TJ Watson Laboratory, Yorktown Heights, New York, February 2020
	
\hspace{-0.75cm} Yahoo! Research, New York City, New York, July 2019

\hspace{-0.75cm} IBM TJ Watson Laboratory, Yorktown Heights, New York, October 2018
	
%\hspace{-0.75cm} Nanjing University, Nanjing, Jiangsu, December 2017

%\hspace{-0.75cm} University of Electronic Science and Technology of China, Chengdu, Sichuan, December 2017

%\hspace{-0.75cm} Zhejiang University, Hangzhou, Zhejiang, November 2017

%\hspace{-0.75cm} Tsinghua University, Beijing, November 2017

\hspace{-0.75cm} Binghamton University, Binghamton, New York, March 2017

\hspace{-0.75cm} Georgia State University, Atlanta, Georgia, March 2017

\hspace{-0.75cm} University of Oregon, Eugene, Oregon, March 2017

\hspace{-0.75cm} Rensselaer Polytechnic Institute, Troy, New York, February 2017

\hspace{-0.75cm} University of Maryland, Baltimore County, Baltimore, Maryland, February 2017

\hspace{-0.75cm} Temple University, Philadelphia, Pennsylvania, January 2017

\hspace{-0.75cm} The Ohio State University, Columbus, Ohio, October 2016

\hspace{-0.75cm} University of Massachusetts Boston, Boston, Massachusetts, November 2015

\end{myindentpar}

\subsection{\sc PhD Students Graduated}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}{\bf Daheng Wang}, \textit{Graduated July 2021} \\
	{Dissertation: \textit{Learning Complementarity and Dynamics for Behavior Modeling}} \\
	{First employment: \textit{Applied Scientist at Amazon.com}}

\hspace{-0.75cm}{\bf Tong Zhao}, \textit{Graduated May 2022} \\
	{Dissertation: \textit{Learning to Augment Graph Data}} \\
	{Awarded Snap Research Fellowship (\$10,000)} \\
	{Awarded Amazon Post-Intern Fellowship (\$10,000 AWS credit)} \\
	{First employment: \textit{Research Scientist at Snap Inc.}}

\end{myindentpar}
	
\subsection{\sc Master Students Graduated}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}{\bf Ms. Xueying Wang}, \textit{Graduated May 2019} \\
	{Thesis: \textit{Improving Information Extraction via Truth Finding with Data-Driven Commonsense}} \\
	{First employment: \textit{Data Scientist at MIT Sloan School of Management}} \\
	{Current employment: \textit{Data Scientist at FedEx}}

\hspace{-0.75cm}{\bf Ms. Bhakti Sharma}, \textit{Graduated July 2020} \\
	{Project: \textit{Review Analysis: Analyzing Sentiment and Predicting Rating Score from Amazon Reviews using BERT}} \\
	{First employment: \textit{Software Engineer at VISO Trust}}

\hspace{-0.75cm}{\bf Jianing Li}, \textit{Graduated November 2020} \\
	{Project: \textit{Empirical Analysis on Training Source-Domain Models for Transfer Learning to Predict Phonon Properties with Electron Properties}}

\end{myindentpar}

\subsection{\sc Past Students Supervised}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}{\bf Eric Zhang}, \textit{Trinity High School Student} (September 2018--July 2020)

\hspace{-0.75cm}{\bf Michael Florin}, \textit{Trinity High School Student} (September 2019--July 2020)

\hspace{-0.75cm}{\bf Ms. Rebekah Fang} and {\bf Ms. Libby Garnett}, \textit{Trinity High School Students} (August 2020--December 2021) \\
	Won the second place in the 2021 Northern Indiana Regional Science and Engineering Fair. Recommended to the 33rd Annual Hoosier Science and Engineering Fair (HSEF).

\hspace{-0.75cm}{\bf Matthew Malir}, \textit{Undergraduate Student} (January--May 2018)
	
\hspace{-0.75cm}{\bf Sebastian Miner}, \textit{Undergraduate Student} (January--May 2018)

\hspace{-0.75cm}{\bf Matthew Schoenbauer}, \textit{Undergraduate Student} (September 2018--May 2019)
	
\hspace{-0.75cm}{\bf Ms. Yuhan (Tina) Wu}, \textit{Undergraduate Student} (September 2018--May 2019)

\hspace{-0.75cm}{\bf Chan Hee Song}, \textit{Undergraduate Student} (September 2019--March 2020)

\hspace{-0.75cm}{\bf Xiangyu Dong}, \textit{Undergraduate Student} (September 2019--July 2020)

\hspace{-0.75cm}{\bf Tianze Zheng}, \textit{Undergraduate Student} (September 2019--July 2020)

\hspace{-0.75cm}{\bf Bo Ni}, \textit{Undergraduate Student} (September 2019--July 2021) \\
	Selected for honorable mention for the Computing Research Association's (CRA) Outstanding Undergraduate Researcher Award for 2021

\hspace{-0.75cm}{\bf Alvin Alaphat}, \textit{Undergraduate Student} (January--May 2020)

\hspace{-0.75cm}{\bf Luke Marushack}, \textit{Undergraduate Student} (January--May 2020)

\hspace{-0.75cm}{\bf Michael Lee}, \textit{Undergraduate Student} (May 2020--May 2021)

\hspace{-0.75cm}{\bf Ms. Ann Hermann}, \textit{Undergraduate Student} (May 2020--August 2021)

\hspace{-0.75cm}{\bf Joseph Kuebler}, \textit{Undergraduate Student} (August--November 2020)

\hspace{-0.75cm}{\bf Facundo Munoz}, \textit{Undergraduate Student} (August--November 2020)

\hspace{-0.75cm}{\bf Fangcong Yin}, \textit{Undergraduate Student} (August--November 2020)

\hspace{-0.75cm}{\bf Jackson Ballow}, \textit{Undergraduate Student} (September 2021--May 2022)

\hspace{-0.75cm}{\bf Ryan Pairitz}, \textit{Undergraduate Student} (January--May 2022)

\hspace{-0.75cm}{\bf Kekoa Wang}, \textit{Undergraduate Student} (January--May 2022)

\hspace{-0.75cm}{\bf Ms. Longqing Chen}, \textit{Undergraduate Student} (September--December 2021)

\hspace{-0.75cm}{\bf Wenhao Yu}, \textit{Visiting Undergraduate Student} (May--August 2018)

\hspace{-0.75cm}{\bf Ms. Yu Shu}, \textit{Visiting Undergraduate Student} (May--August 2018)

\hspace{-0.75cm}{\bf Chuchen Deng}, \textit{Visiting Undergraduate Student} (May--August 2019)

\hspace{-0.75cm}{\bf Yihong Ma}, \textit{Visiting Undergraduate Student} (May--August 2019)

\hspace{-0.75cm}{\bf Xin Liu}, \textit{Visiting Undergraduate Student} (July--August 2019)

\hspace{-0.75cm}{\bf Wei Peng}, \textit{Visiting Undergraduate Student} (July--August 2019)

\hspace{-0.75cm}{\bf Ms. Mengxia Yu}, \textit{Visiting Undergraduate Student} (July--August 2019)

\hspace{-0.75cm}{\bf Ms. Kaifeng Yu}, \textit{Visiting Undergraduate Student} (July--August 2019)

\hspace{-0.75cm}{\bf Zhihan Zhang}, \textit{Visiting Undergraduate Student} (July--August 2019)

\hspace{-0.75cm}{\bf Ms. Yang Zhou}, \textit{Visiting Undergraduate Student} (July--August 2019)

\hspace{-0.75cm}{\bf Zaitang Li}, \textit{Visiting Undergraduate Student} (September 2019--July 2020)

\hspace{-0.75cm}{\bf Ms. Xueying Wang}, \textit{Master Student} (January 2018--May 2019)

\hspace{-0.75cm}{\bf Ms. Bhakti Sharma}, \textit{Master Student} (May--July 2020)

\hspace{-0.75cm}{\bf Jianing Li}, \textit{Master Student} (September 2019--November 2020)

\hspace{-0.75cm}{\bf Zijian Hu}, \textit{Visiting Master Student} (July--August 2019)

\hspace{-0.75cm}{\bf Tianwen Jiang}, \textit{Visiting PhD Student} (September 2018--August 2019)

\end{myindentpar}

\subsection{\sc Current Students Supervised}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}{\bf Yunxiang (Ryan) Yan}, \textit{Undergraduate Student} (since September 2021)

\hspace{-0.75cm}{\bf Weike Fang}, \textit{Undergraduate Student} (since January 2022)

\hspace{-0.75cm}{\bf Qingkai Zeng}, \textit{Ph.D. Candidate} (since January 2018) \\
	{Thesis: \textit{Improving Scientific Information Extraction with Text Generation}} \\
	{Received Kaneb Center Outstanding TA Award}

\hspace{-0.75cm}{\bf Wenhao Yu}, \textit{Ph.D. Candidate} (since July 2019) \\
	{Notre Dame CSE Select Fellowship}

\hspace{-0.75cm}{\bf Ms. Lingbo Tong}, \textit{Ph.D. Student} (since August 2020) \\
	{Joint Ph.D. in Psychology and Computer Science \& Engineering}

\hspace{-0.75cm}{\bf Ms. Mengxia Yu}, \textit{Ph.D. Student} (since August 2020) \\
	{Notre Dame CSE Select Fellowship}

\hspace{-0.75cm}{\bf Gang Liu}, \textit{Ph.D. Student} (since August 2021)

\hspace{-0.75cm}{\bf Zhihan Zhang}, \textit{Ph.D. Student} (since August 2021)

\hspace{-0.75cm}{\bf Noah Ziems}, \textit{Ph.D. Student} (since May 2022)

\hspace{-0.75cm}{\bf Eric Inae}, \textit{Ph.D. Student} (since August 2022) \\
	{Notre Dame Dean's Fellowship}

\hspace{-0.75cm}{\bf Hy Dang}, \textit{Ph.D. Student} (since August 2022)

\hspace{-0.75cm}{\bf Ms. Nandini Banerjee}, \textit{Ph.D. Student} (since August 2022)

\end{myindentpar}

\subsection{\sc Teaching Courses}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}{\bf CS 412 Introduction to Data Mining}, \textit{University of Illinois} (Summer 2017)
	
\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Fall 2017)

\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Spring 2018)

\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Fall 2018)

\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Fall 2019)

\hspace{-0.75cm}{\bf CSE 60326 Computational Behavior Modeling}, \textit{University of Notre Dame} (Spring 2020)

\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Fall 2020)

\hspace{-0.75cm}{\bf CSE 60326 Computational Behavior Modeling}, \textit{University of Notre Dame} (Spring 2021)

\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Fall 2021)

\hspace{-0.75cm}{\bf CSE 60326 Computational Behavior Modeling}, \textit{University of Notre Dame} (Spring 2022)

\hspace{-0.75cm}{\bf CSE 40647/60647 Data Science}, \textit{University of Notre Dame} (Fall 2022)

\end{myindentpar}

\subsection{\sc Professional Activities}
\vspace{-0.4cm} \line(1,0){370} \vspace{-0.1cm}

\begin{myindentpar}{0.75cm}

\hspace{-0.75cm}{\bf Governmental Service}

{\small

\textcolor{white}{} NIH DABP-PSE-IRAP Panelist (2021) \\
\textcolor{white}{} NSF CISE Panelist (2020, 2022)
}

\hspace{-0.75cm}{\bf Departmental Service}

{\small

\textcolor{white}{} Graduate admission committee at ND CSE (since 2017)
}

\hspace{-0.75cm}{\bf Ph.D. Dissertation Committee}

{\small

\textcolor{white}{} {\bf Dr. Maria Glenski}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Yuan Gong}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Chao Huang}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Suhansanu Kumar}, UIUC Computer Science \\
\textcolor{white}{.}{\bf Dr. Ann Franchesca Laguna}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Qi Li}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Zhiyu Liu}, Notre Dame Electrical Engineering \\
\textcolor{white}{.}{\bf Dr. Kenton Murray}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Alireza Partovi}, Notre Dame Electrical Engineering \\
\textcolor{white}{.}{\bf Dr. Mandana Saebi}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Munira Syed}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Pamela Bilo Thomas}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Tianchen Wang}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Xian Wu}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Chuxu Zhang}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Hao Zheng}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Dr. Shenglong Zhu}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Nicholas Botzer}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Justus Hibshman}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Peixian Liang}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Jinfeng Lin}, Notre Dame Comp. Sci. \& Eng. \\
\textcolor{white}{.}{\bf Guoqiang Liu}, Notre Dame Biology \\
\textcolor{white}{.}{\bf Qing Lu}, Notre Dame Comp. Sci. \& Eng.
}

%\hspace{-0.75cm}{\bf Editorial Board} \\
% XXXX

\hspace{-0.75cm}{\bf Organizing Committee}

{\small

\hspace{-0.75cm}\textit{2022}\textcolor{white}{.}Co-Chair, Workshop on Knowledge Discovery and Data Mining in IT Operations (BigData-IT) at IEEE BigData

\hspace{-0.75cm}\textit{2022}\textcolor{white}{.}Co-Chair, Workshop on Misinformation and Misbehavior Mining on the Web (MIS2) at ACM SIGKDD Conference on Knowledge Discovery and Data Mining (KDD)

\hspace{-0.75cm}\textit{2022}\textcolor{white}{.}Doctoral Consortium Chair, ACM International Conference on Web Search and Data Mining (WSDM)

\hspace{-0.75cm}\textit{2019}\textcolor{white}{.}Publication Chair, ACM International Conference on Knowledge Management (CIKM) \\
\textcolor{white}{.}Publicity Chair, Int'l Conf. on Computational Data and Social Networks (CSoNet)

\hspace{-0.75cm}\textit{2018}\textcolor{white}{.}Co-Chair, Workshop on Misinformation and Misbehavior Mining on the Web (MIS2) at International Conference on Web Search and Data Mining (WSDM)

\hspace{-0.75cm}\textit{2016}\textcolor{white}{.}Co-Chair, Special session on Big Behavioral Data Analytics at IEEE International Conference on Data Science and Advanced Analytics (DSAA)

}

\hspace{-0.75cm}{\bf (Senior) Program Committee / Reviewer / (Senior) Area Chair}

{\small

\hspace{-0.75cm}ACM SIGKDD Int'l Conf. on Knowledge Discovery and Data Mining (KDD): \\
(PC: 2018--2021, SPC: 2022)

\hspace{-0.75cm}ACM International Conference on Knowledge Management (CIKM): \\
(PC: 2017--2019, SPC: 2020--2022)

\hspace{-0.75cm}AAAI Conference on Artificial Intelligence (AAAI): \\
(PC: 2017--2021, SPC: 2022)

\hspace{-0.75cm}International Joint Conference on Artificial Intelligence (IJCAI): \\
(SPC: 2021)

\hspace{-0.75cm}The Web Conference (TheWebConf/WWW): \\
(PC: 2018--2022)

\hspace{-0.75cm}International Conference on Web Search and Data Mining (WSDM): \\
(PC: 2019--2022)

\hspace{-0.75cm}Asia-Pacific Chapter of the Association for Computational Linguistics (AACL): \\
(SAC: 2022)

\hspace{-0.75cm}Annual Meeting of the Association for Computational Linguistics (ACL): \\
(Reviewer: 2020--2022)

\hspace{-0.75cm}Conference on Empirical Methods in Natural Language Processing (EMNLP): \\
(Reviewer: 2018--2020; AC: 2021)

\hspace{-0.75cm}Conference on Neural Information Processing Systems (NeurIPS): \\
(Reviewer: 2020--2022)

\hspace{-0.75cm}International Conference on Learning Representations (ICLR): \\
(Reviewer: 2021)

\hspace{-0.75cm}SIAM Conference on Data Mining (SDM): \\
(PC: 2018--2021)

\hspace{-0.75cm}International Conference on Artificial Intelligence in Medicine (AIME): \\
(SPC: 2020)

}

%\hspace{-0.75cm}{\bf Editorial Board}

\hspace{-0.75cm}{\bf Journal Reviewer}

{\small

%IEEE Access (\textit{Access}) \\
%Artificial Intelligence Journal (\textit{AI Journal}) \\
%Decision Sciences Journal (\textit{DSJ}) \\
Data Mining and Knowledge Discovery (\textit{DAMI}) \\
%Frontiers of Computer Science (\textit{FCS}) \\
%International Journal of Information Technology and Decision Making (\textit{IJITDM}) \\
Information Sciences (\textit{INS}) \\
Information Systems (\textit{InfoSys}) \\
Information Processing and Management (\textit{IPM}) \\
%IEEE Intelligent Systems (\textit{IS}) \\
%Journal of Computers (\textit{JCP}) \\
%Journal of Machine Learning Research (\textit{JMLR}) \\
%INFORMS Journal on Computing (\textit{JOC}) \\
Knowledge and Information Systems (\textit{KAIS}) \\
Neurocomputing (\textit{NEUCOM}) \\
PLOS ONE (\textit{PlosOne}) \\
%Pattern Recognition (\textit{PR}) \\
Scientific Reports (\textit{SciReports}) \\
IEEE Transactions on Big Data (\textit{TBD}) \\
%IEEE Transactions on Information Forensics and Security (\textit{TIFS}) \\
%KSII Transactions on Internet and Information Systems (\textit{TIIS}) \\
ACM Transactions on Intelligent Systems and Technology (\textit{TIST}) \\
ACM Transactions on Knowledge Discovery from Data (\textit{TKDD}) \\
IEEE Transactions on Knowledge and Data Engineering (\textit{TKDE}) \\
Transactions on Information Systems (\textit{TOIS}) \\
%ACM Trans. on Multimedia Comp. Comm. and App. (\textit{TOMCCAP}) \\
IEEE Transactions on Neural Networks and Learning Systems (\textit{TNNLS})
%World Wide Web Journal (\textit{WWWJ})

}

\end{myindentpar}

\end{document}

