\documentclass[11pt]{article}

\usepackage{fancyhdr,graphicx,multicol,paralist,times,url,wrapfig}

\setcounter{page}{1}

\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.85in}
\setlength{\oddsidemargin}{-0.2in}
\pagestyle{empty}

\begin{document}

\noindent {1009 West Clark Street \#201} \\
\noindent {Urbana, IL 61801}

\vskip 0.15in

\noindent {November 15, 2016}

\vskip 0.15in

\noindent {XXX Search Committee} \\
\noindent {XXX University} \\
\noindent {XXX XXX Street} \\
\noindent {XXX, XX XXXXX}

\vskip 0.10in

\noindent {Dear Members of the Search Committee:}

\vskip 0.15in

\noindent {I am writing to apply for the position of [Assistant Professor] in [Computer Science] beginning [Fall 2017], as advertised on [your department website]. I am currently a postdoctoral research associate at the University of Illinois at Urbana-Champaign (UIUC). I obtained my Ph.D. degree in Computer Science at Tsinghua University, China in July 2015. I respectfully submit this letter of application, for I believe my experiences and commitment to research and teaching make me well qualified to meet the needs of [XXX's XXX program].}

\vskip 0.10in

\noindent {My rich academic training prepares me to be an effective and focused researcher. I have been devoted to the research of Data-Driven Behavioral Analytics towards intelligence and trustworthiness for more than six years. My doctoral dissertation, that is entitled ``Modeling Complex Behaviors in Social Media'', investigates the data-driven methodology from observation to representation, and to the development of computational models for recommendation and fraud/spam detection. It covers how to model social spatio-temporal contexts (directed by my advisor Prof. Shiqiang Yang) and how to capture suspicious intentions (directed by Prof. Christos Faloutsos during my visit to Carnegie Mellon University). During my postdoctoral research with Prof. Jiawei Han, I tackle the problem of structuring the unstructured behavioral content/text into information networks of entities, attributes and relationships, and integrating the networks with behavioral analysis for accuracy and interpretability. I have delivered 15 papers as the first author at top-tier conferences and journals including three at ACM SIGKDD and three in IEEE Trans. on Knowledge and Data Engineering as well as tutorials in IEEE ICDM and ACM CIKM. I am extremely interested in an opportunity of continuing my research, conducting cross-disciplinary studies, organizing professional service activities and creating real-world impact with data-driven techniques.}

\vskip 0.10in

\noindent {Besides the research, I have fruitful training on proposal writing and project leading in UIUC. I wrote 8 pages of 15 of the NSF III Small proposal ``Multi-Dimensional Structuring, Summarizing and Mining of Social Media Data'' (PI: Professor Jiawei Han) which was accepted in August 2016. I am the major supported member in this NSF IIS 16-18481 program. I am also leading the project ``Distributed, User-Oriented Multi-Scale Network Summarization and Online Analytical Processing'' in Year 8/9 on the UIUC side collaborating with Army Research Lab in the Network Science Collaborative Technology Alliance.}

\vskip 0.10in

\noindent {During my graduate training, I was fortunate to have served as a teaching assistant in two courses, and during my postdoctoral training, I was occasionally a substitute lecturer for an undergraduate-level course and a guest lecturer for two graduate-level courses. I found that my professional experience is useful in motivating and assisting students with projects and assignments. These experiences have built my confidence and interest in teaching and I look forward to the opportunity to not only teach existing courses, but also work to develop new ones.}

\vskip 0.10in

\noindent {I would enjoy discussing this position with you in the weeks to come. In the meantime, I am enclosing my Curriculum Vitae and statement of teaching and research interests. Letters of recommendation will arrive under separate cover. If you require any additional materials or information, I am happy to supply it. Thank you very much for your time and consideration.}

\vskip 0.15in

\noindent {Sincerely,}

\vskip 0.15in

\noindent {Meng Jiang}

\end{document}


