\documentclass[11pt]{article}

\usepackage{fancyhdr,graphicx,multicol,paralist,times,url,wrapfig}

\setcounter{page}{1}

\setlength{\textwidth}{6.8in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.85in}
\setlength{\oddsidemargin}{-0.2in}
\pagestyle{empty}

\begin{document}

\begin{center}
{\LARGE \bf Diversity Statement}
\end{center}

\noindent {1009 West Clark Street \#201} \\
\noindent {Urbana, IL 61801}

\vskip 0.15in

\noindent {November 21, 2016}

\vskip 0.15in

\noindent {XXX Search Committee} \\
\noindent {XXX University} \\
\noindent {XXX XXX Street} \\
\noindent {XXX, XX XXXXX}

\vskip 0.15in

\noindent {Dear Members of the Search Committee:}

\vskip 0.20in

\noindent {I am writing to apply for the faculty position in [Computer Science] beginning [Fall 2017] with my commitment to embracing the rich cultural, racial, geographic, economic and social diversity of the campus community. I would like to provide my perspectives on my past, present, and future aspirations and contributions to promoting equity, inclusion and diversity in my professional career.}

\vskip 0.10in

\noindent {When I was pursuing my Ph.D. in Tsinghua University, China, I was a social activity coordinator in the International Student \emph{Master in Advanced Computing} Program as well as a Teaching Assistant for the course \emph{Advanced Multimedia Technologies}. In the Year 2013, the program has 8 oversea students who come from 6 countries such as Myanmar, Malaysia, Indonesia, Zimbabwe, Malawi, and United States. I have enjoyed the focus on ensuring them understand the course material and sharing various cultures. One of the excellent students is now a Ph.D. candidate in Computer Science at University of Melbourne.}

\vskip 0.10in

\noindent {During my postdoctoral training in University of Illinois at Urbana-Champaign (UIUC), I advised three teams (24 undergraduate students) in the course project of \emph{UIUC-CS412 An Introduction to Data Mining}. I organized the team-leader election in which each candidate presented their ideas of solving the research problem and distributing the workload to the teammates. Two of the teams have smart and excellent women students as the leaders, and all the three teams have fruitful experiences and solid results in the project. Besides this, I am currently mentoring a woman graduate student and we collaborated in several submissions to top-tier conferences.}

\vskip 0.10in

\noindent {In this statement, I commit to using a faculty position to be a force of enlightenment and change by opening up opportunities to students who may have never known of the intellectual and life options that abound at the university. I am active in creating and joining programs that provide access and establish a pipeline in disciplines for students in traditionally underrepresented groups. I am willing to enrich the classroom environment through exposure to new perspectives on cultures, beliefs, practices, tolerance, acceptance, and a welcoming climate. As what I have done in the past years, I encourage the leadership in which diversity is welcomed, fostered, and celebrated. I am positive to mentor students from traditionally underrepresented groups and at-risk students to provide the guidance needed to help ensure their academic experience is a welcoming and positive one.}

\vskip 0.10in

\noindent {I would like to implement an open environment immediately I joined the university. I would like to organize activities that encourage the students in the underrepresented groups to lead projects and academic articles. I promote my idea that \emph{confidence} and \emph{communication} can bridge people of different backgrounds into one world.}

\vskip 0.30in

\noindent {Sincerely,}

\vskip 0.25in

\noindent {Meng Jiang}

\end{document}


